---
title: "Food Bank Distribution"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(sf)
datathon_df <- readRDS("../data/datathon.rds")
```

## Example ggplot graph

```{r}
datathon_df %>%
  ggplot() +
  geom_point(aes(census_B08201_001, census_B08201_002)) +
  labs(x = "Total households in county", y = "Households with no vehicles")
```

## Example choropleth map

```{r}
datathon_df %>%
  mutate(
    pct_no_vehicle = 100 * census_B08201_002 / census_B08201_001
  ) %>%
  ggplot() +
  geom_sf(aes(fill = pct_no_vehicle)) +
  labs(title = "% of households with no vehicle")
```

```{r}
datathon_df %>%
  st_drop_geometry() %>%
  select(census_NAME,FOOD_BANKS18) %>%
  arrange(desc(FOOD_BANKS18))
```
```{r}
datathon_df %>%
  ggplot() +
  geom_sf(aes(fill = FOOD_BANKS18)) +
  labs(title = "# of Food Banks")
```
Here is a graph that displays the amount of food banks in Virginia counties in the year 2018. Places highlighted and have food banks are Spotsylvania, Augusta, Hampton, Norfolk, Salem, and Richmond counties. 

We see here that the food banks are generally located around the center of Virginia rather than the perimeter. Overall, there is a very low number of food banks (maximum being 1 in each county) within Virginia in 2018.
