---
title: "Grocery Access"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(sf)
library(leaflet)
library(plotly)

df <- readRDS("../data/datathon.rds") %>%
  mutate(
    area_sq_meter = as.numeric(st_area(geometry)),
    area_sq_miles = 0.00000038610215855 * area_sq_meter,
    grocery_density = GROC16 / area_sq_miles,
    snaps_density = SNAPS17 / area_sq_miles,
    seniors_in_poverty = census_B17020_015 + census_B17020_016 + census_B17020_017,
    senior_poverty_pctpop = seniors_in_poverty / census_B17020_001
  )
```

# Overview

Inputs {.sidebar}
-------------------------------------

**Team Peterson (21)**

*Department of Computational and Data Sciences*

*George Mason University*

Team members:

* Adjoa Dofour
* Dominic White
* Geda Gelana
* Jessica Nguyen
* Meti Gebre


Column {data-width=650}
-----------------------------------------------------------------------

### The Last Mile Problem

* 

Column {data-width=350}
-----------------------------------------------------------------------

### Vehicles

```{r}
valueBox(
  "6.1%",
  caption = "Percentage of Virginia households without a vehicle", 
  color = "primary"
  )
```

### ...

```{r}
# df %>%
#   st_drop_geometry() %>%
#   summarize(
#     mean(PCT_LACCESS_POP15, na.rm=TRUE),
#     sum(LACCESS_POP15, na.rm=TRUE)
#   )

valueBox(
  "17.9%",
  caption = "Average percentage of Virginians in a country with low access to a store", 
  color = "warning"
  )
```

### ?

```{r}
valueBox(
  "1,443,895",
  caption = "Number of Virginians with low access to a store", 
  color = "danger"
  )
```

# Who has no car?

Column {data-width=550}
-----------------------------------------------------------------------

<!-- ### ? -->

<!-- ```{r} -->
<!-- p <- df %>% -->
<!--   ggplot(aes( -->
<!--       x = POVRATE15, -->
<!--       y = `PCT_LACCESS_HHNV15` -->
<!--     )) + -->
<!--   geom_point() + -->
<!--   geom_smooth(method = "lm", se=F) + -->
<!--   labs( -->
<!--     x = "Poverty rate", -->
<!--     y = "% households no vehicle and low access to store" -->
<!--   ) -->
<!-- ggplotly(p) -->
<!-- ``` -->

Column {data-width=450}
-----------------------------------------------------------------------

### Correlation between low access SNAP households and vehicle-less households

```{r}
p <- df %>%
  ggplot(aes(
      x = `census_S2201_C04_001`,
      y = 100 * census_B08201_002 / census_B08201_001
    )) +
  geom_point() +
  geom_smooth(method = "lm", se=F) +
  labs(
    x = "% SNAP households",
    y = "% households with no vehicle"
  )
ggplotly(p)
```



# Where are stores?


Column {data-width=700}
-----------------------------------------------------------------------

### Stores accepting SNAP per square mile

```{r}
# states <- geojsonio::geojson_read("json/us-states.geojson", what = "sp")

bins <- c(0, 0.05, 0.1, 0.2, 0.6, 1, 2, 4, Inf)
pal <- colorBin("YlOrRd", domain = df$snaps_density, bins = bins)

labels <- sprintf(
  "<strong>%s</strong><br/>%g stores / mi<sup>2</sup>",
  df$census_NAME, df$snaps_density
) %>% lapply(htmltools::HTML)

leaflet(df) %>%
  setView(-79.2, 37.5, 7) %>%
  addProviderTiles("CartoDB.Positron") %>%
  addPolygons(
    fillColor = ~pal(snaps_density),
    weight = 2,
    opacity = 1,
    color = "white",
    dashArray = "3",
    fillOpacity = 0.7,
    highlightOptions = highlightOptions(
      weight = 5,
      color = "#666",
      dashArray = "",
      fillOpacity = 0.7,
      bringToFront = TRUE),
    label = labels,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto")) %>%
  addLegend(pal = pal, values = ~snaps_density, opacity = 0.7, title = NULL,
    position = "topleft")
```

<!-- Column {data-width=300} -->
<!-- ----------------------------------------------------------------------- -->

<!-- ### ? -->

<!-- ```{r} -->

<!-- ``` -->

<!-- ### ... -->

<!-- ```{r} -->

<!-- ``` -->




# Where are food deserts?

Column
-----------------------------------------------------------------------

### Number of SNAP households more than 10 miles from a store 

```{r}
bins <- c(0, 50, 100, 200, 300, 400, Inf)
pal <- colorBin("YlOrRd", domain = df$lasnap10, bins = bins)

labels <- sprintf(
  "<strong>%s</strong><br/>%g households",
  df$census_NAME, df$lasnap10
) %>% lapply(htmltools::HTML)

leaflet(df) %>%
  setView(-79.2, 37.6, 6) %>%
  addProviderTiles("CartoDB.Positron") %>%
  addPolygons(
    fillColor = ~pal(lasnap10),
    weight = 2,
    opacity = 1,
    color = "white",
    dashArray = "3",
    fillOpacity = 0.7,
    highlightOptions = highlightOptions(
      weight = 5,
      color = "#666",
      dashArray = "",
      fillOpacity = 0.7,
      bringToFront = TRUE),
    label = labels,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto")) %>%
  addLegend(pal = pal, values = ~lasnap10, opacity = 0.7, title = NULL,
    position = "topleft")
```

Column
-----------------------------------------------------------------------

### Number of households without a vehicle more than 10 miles from a store 

```{r}
bins <- c(0, 25, 50, 75, 100, 200, 300, Inf)
pal <- colorBin("YlOrRd", domain = df$lahunv10, bins = bins)

labels <- sprintf(
  "<strong>%s</strong><br/>%g households",
  df$census_NAME, df$lahunv10
) %>% lapply(htmltools::HTML)

leaflet(df) %>%
  setView(-79.2, 37.6, 6) %>%
  addProviderTiles("CartoDB.Positron") %>%
  addPolygons(
    fillColor = ~pal(lahunv10),
    weight = 2,
    opacity = 1,
    color = "white",
    dashArray = "3",
    fillOpacity = 0.7,
    highlightOptions = highlightOptions(
      weight = 5,
      color = "#666",
      dashArray = "",
      fillOpacity = 0.7,
      bringToFront = TRUE),
    label = labels,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto")) %>%
  addLegend(pal = pal, values = ~lahunv10, opacity = 0.7, title = NULL,
    position = "topleft")
```



# What about seniors?

```{r}
# library(tidycensus)
# v19 <- tidycensus::load_variables(2019,"acs5")
# poverty <- v19 %>%
#   filter(str_starts(name, "B17020"))
```


```{r}
# colnames(df)
```


Column
-----------------------------------------------------------------------

### Correlation between seniors on SNAP and low access SNAP participants

```{r}
p <- df %>%
  ggplot(aes(
    PCT_LACCESS_SENIORS15, PCT_LACCESS_SNAP15
  )) + 
  geom_point() +
  geom_smooth(method="lm", se = F) +
  labs(
    x = "% of seniors on SNAP",
    y = "% SNAP recipients with low access"
  )
ggplotly(p)
```

## Columns

### Where are seniors with low access

```{r}
bins <- c(0, 100, 200, 300, 500, 1000, Inf)
pal <- colorBin("YlOrRd", domain = df$LACCESS_SENIORS15, bins = bins)

labels <- sprintf(
  "<strong>%s</strong><br/>%g people",
  df$census_NAME, df$LACCESS_SENIORS15
) %>% lapply(htmltools::HTML)

leaflet(df) %>%
  setView(-79.2, 37.6, 6) %>%
  addProviderTiles("CartoDB.Positron") %>%
  addPolygons(
    fillColor = ~pal(LACCESS_SENIORS15),
    weight = 2,
    opacity = 1,
    color = "white",
    dashArray = "3",
    fillOpacity = 0.7,
    highlightOptions = highlightOptions(
      weight = 5,
      color = "#666",
      dashArray = "",
      fillOpacity = 0.7,
      bringToFront = TRUE),
    label = labels,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto")) %>%
  addLegend(pal = pal, values = ~LACCESS_SENIORS15, opacity = 0.7, title = NULL,
    position = "topleft")
```

# Solutions

## Column

### Possible policy solutions

* Expand use of SNAP in online grocery shopping.

* Incentivize delivery services to delivery to SNAP recipients at low/no cost.

  * Target participents without vehicles, such as seniors.

